---
title: "Health Condition Benchmarking"
output: 
  html_notebook: 
    highlight: pygments
    theme: cosmo
---

# Project Notebook

__Purpose:__ Show chronic health condition prevelance benchmarked against local, state, and national data.  

* __Goals & Outcomes:__ 
    1. Define controlled versus uncontrolled disease states.
    2. Define logic in using the defined states with self-reported condition status. 
    3. Run 2016 data through algorithm and compare to local, state and national data.
    4. Run previous years data through algorithm and visualize population change.
    5. Create SQL for logic/algorithm to use with NGH Data Warehouse.
    6. Integrate Pre-disease state aggregation into analysis. 
    
<hr>

## 1. Define Controlled vs Un-controlled states

 __Condition Definitions:__ 
 
## 2. Process Logic

 __Decision Tree:__

## 3. 2016 Biometric, PHA, and Claims Data

### Data Sources:
Below are the data source locations and parameters used for this project.

+ PHA Detail (https://reports.cernerwellness.com)
    + **Baseline Start Date:** 09/29/2015
    + **Baseline End Date:** 09/26/2016
    + **Member Status:** Both
    + **Temp Accounts:** Both
    + **Input Labels:** Show
    + **Cohort:** No

+ Biometric Detail (https://reports.cernerwellness.com)
    + **Baseline Start Date:** 09/29/2015
    + **Baseline End Date:** 09/26/2016
    + **Member Status:** Both
    + **Temp Accounts:** Both
    + **Input Labels:** Show
    + **Cohort:** No

+ Provider Intelligence Claims Data (https://pophealthproducts.verscend.com)
    + **Report Name:** (CD018) Disease Analysis by Members
    + **Disease:** Diabetes, Hypertension, Hyperlipidemia
    + **Analysis Period:** Full Cycle (Jul 13 thru Sep 16)
    + **Exclude:** None
    + **Member List:** None
        

### Provider Intelligence - Disease Definitions:
The following are the diagnosis and proceedure codes used by Verscend (formerly Verisk Health) used to create disease registries for Norton medical insurance participants. - Last Updated: (12/28/2016)

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(plotly)
library(reshape2)
library(RColorBrewer)
library(dplyr)
library(knitr)
library(scales)
require(tidyverse)
require(viridis)

DiagProcCode <- c("Z9641", "Z8631", "Z794", "V5867", "V4585", "T85694A", "O24813", "O24313", "O24312", "O2413", "O2412", "O24113", "O24112", "O24111", "O2403", "O24019", "O24013", "O24012", "O24011", "J1817", "J1815", "G0109", "G0108", "E139", "E138", "E1365", "E1311", "E1310", "E119", "E118", "E1169", "E1165", "E11649", "E11628", "E11622", "E11621", "E11610", "E1159", "E1152", "E1151", "E1149", "E1143", "E1142", "E1140", "E1139", "E1136", "E11359", "E11351", "E11349", "E11341", "E11339", "E11331", "E11329", "E11321", "E11319", "E1129", "E1122", "E1121", "E1100", "E109", "E108", "E1069", "E1065", "E10649", "E10621", "E1059", "E1049", "E1042", "E1041", "E1040", "E10359", "E10351", "E10349", "E10339", "E10331", "E10329", "E10321", "E10319", "E1022", "E1021", "E1010", "E0910", "E089", "E08621", "E0841", "E0829", "E0821", "E0810", "E0800", "E0784", "E0607", "A9278", "A9277", "A9276", "A9274", "A5513", "A5512", "A5507", "A5501", "A5500", "A4253", "A4232", "A4231", "A4230", "95251", "83037", "64804", "64803", "64802", "64801", "64800", "36641", "36207", "36206", "36205", "36204", "36202", "36201", "3572", "3060F", "3046F", "3045F", "3044F", "25093", "25092", "25091", "25090", "25083", "25082", "25081", "25080", "25072", "25071", "25070", "25063", "25062", "25061", "25060", "25053", "25052", "25051", "25050", "25043", "25042", "25041", "25040", "25033", "25032", "25031", "25030", "25022", "25013", "25012", "25011", "25010", "25003", "25002", "25001", "25000", "24980", "24960", "24950", "24911", "24901", "24900", "2028F")

Type <- c("ICD10", "ICD10", "ICD10", "ICD9", "ICD9", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "HCPCS", "CPT4", "CPT4", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "CPT4", "CPT4", "CPT4", "CPT4", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "CPT4")

diabetes <- data.frame(DiagProcCode,Type)

DiagProcCode <- c("O119", "O113", "O112", "O1093", "O1092", "O10919", "O10913", "O10912", "O10911", "O10419", "O10413", "O10013", "O10012", "I674", "I159", "I158", "I151", "I129", "I120", "I119", "I10", "H35033", "4372", "40599", "40591", "40511", "40490", "40401", "40391", "40390", "40311", "40310", "40300", "40291", "40290", "40210", "4019", "4011", "4010")

Type <- c("ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9")


hypertension <- data.frame(DiagProcCode,Type)


DiagProcCode <- c("E882", "E789", "E786", "E785", "E784", "E783", "E782", "E781", "E780", "2729", "2728", "2725", "2724", "2722", "2721", "2720")

Type <- c("ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD10", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9", "ICD9")

hyperlipidemia <- data.frame(DiagProcCode,Type)

```

##### Provider Intelligence (TG105a) Diabetes Codes
```{r, echo=FALSE}
diabetes
```

##### Provider Intelligence (TG105a) Hypertension Codes
```{r, echo=FALSE}
hypertension
```

##### Provider Intelligence (TG105a) Hyperlipidemia Codes
```{r, echo=FALSE}
hyperlipidemia
```


